Instructions for \confname{} Proceedings

### 2019-05-07 papers/EMNLP2019/analysis.tex
intro quite decent; minor fixes in other sections

\begin{itemize}
\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
\item \textbf{hyponymy}: e.g.\ man vs. person
\item \textbf{co-hyponymy}: e.g.\ chicken vs. dinner, swan vs. goose
\item \textbf{no relation}: e.g.\  desk vs. apple
\end{itemize}

\begin{table}
\small
\begin{tabular}{llll}
\toprule
        relation & \% types & \% tokens & av. depth \\
\midrule
 co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
    hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
        synonymy &  0.015 &  0.121 &       1.000 \\
\bottomrule
\end{tabular}
\caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?} \gbt{yes, please. Maybe do rows domains, columns lexical relations (synymymy, hyponymy, co-hyponymy, other, not in wordnet), with subcolumns for types and tokens? And do percentages over rows -- for each domain, how many of the variants we find fall into each of the classes. This way we'll be able to see differences across domains.}}
\label{tab:rel}
\end{table}

@@

\gbt{@Sina, for this section/my analysis, I'd need csvs (or some code that builds dataframes) containing the following:}

  \begin{enumerate}
  \item Dataframe for images: for each image,
    \begin{itemize}
    \item top -- top name
    \item \% top
    \item SN -- snodgrass agreement
    \item =VG
    \item dictionary or similar with names and counts
    \end{itemize}
  \item Dataframe for name variants: for each variant pair,
    \begin{itemize}
    \item top name
    \item variant
    \item frequency of the pair
    \item domain of top
    \item domain of variant (one of ours or ``OTHER'' if not in any of them?)
    \item relationship in wordnet, one of: synonymy, hyponymy, co-hyponymy, other, not in wordnet (agree? the latter means ``one of the elements not in wordnet'')
    \end{itemize}
  \end{enumerate}

>>>>

\begin{itemize}
\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
\item \textbf{hyponymy}: e.g.\ man vs. person
\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
\item \textbf{no relation}: e.g.\  desk vs. apple
\end{itemize}

\begin{table}

\begin{tabular}{lll}
\toprule
       relation &  types & tokens \\
\midrule
synonymy &  0.01 &  0.09 \\
co-hyponymy &  0.03 &  0.07 \\
hypernymy &  0.06 &  0.35 \\
not-covered &  0.19 &  0.04 \\
crossclassified &  0.70 &  0.47 \\
\bottomrule
\end{tabular}
% \small
% \begin{tabular}{llll}
% \toprule
%         relation & \% types & \% tokens & av. depth \\
% \midrule
%  co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
%     hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
%         synonymy &  0.015 &  0.121 &       1.000 \\
% \bottomrule
% \end{tabular}
\caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?} \gbt{yes, please. Maybe do rows domains, columns lexical relations (synymymy, hyponymy, co-hyponymy, other, not in wordnet), with subcolumns for types and tokens? And do percentages over rows -- for each domain, how many of the variants we find fall into each of the classes. This way we'll be able to see differences across domains.}}
\label{tab:rel}
\end{table}

@@

\gbt{@Sina, for this section/my analysis, I'd need csvs (or some code that builds dataframes) containing the following (see commented text):}

  % \begin{enumerate}
  % \item Dataframe for images: for each image,
  %   \begin{itemize}
  %   \item top -- top name
  %   \item \% top
  %   \item SN -- snodgrass agreement
  %   \item =VG
  %   \item dictionary or similar with names and counts
  %   \end{itemize}
  % \item Dataframe for name variants: for each variant pair,
  %   \begin{itemize}
  %   \item top name
  %   \item variant
  %   \item frequency of the pair
  %   \item domain of top
  %   \item domain of variant (one of ours or ``OTHER'' if not in any of them?)
  %   \item relationship in wordnet, one of: synonymy, hyponymy, co-hyponymy, other, not in wordnet (agree? the latter means ``one of the elements not in wordnet'')
  %   \end{itemize}
  % \end{enumerate}

### 2019-05-07 papers/EMNLP2019/data-collection.tex
intro quite decent; minor fixes in other sections

\section{Data Collection}
\label{sec:task}

%describe the YouNameIt task here

describe the task here

\subsection{Visual Genome data}

\gbt{START to be refined -- taken from sivl submission as is}

\vgenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.

\begin{itemize}
     		\item[(1)] \textbf{Specific categories}: are not available, as object categories and names are not consistently annotated (and even conflated)
				\item[(2)] \textbf{Exhaustive annotations}: are available, which is a huge advantage of this data sets
		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)

\end{itemize}
\gbt{END to be refined -- taken from sivl submission as is}

\cs{START @ GBT}
\subsection{Sampling of Instances (Images/Objects)}
Since our work connects research on object naming in computer vision and in psycholinguistics/cognitive science, we aimed at collecting a relatively large amount of naturalistic images (\textit{instances}) that depict objects of frequent classes/names in visual genome, which, at the same time, have been frequently/commonly studied in the psycholinguistic literature. 
%Criteria: From CV: select images depicting objects with relatively frequent names; From CogSci: select objects which have been frequently studied in cognitive science/psychological norming studies; we chose McRae et al. as basis.
We chose the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of norming studies (REFS).
In contrast to the latter, the McRae norms do not contain names of the \textsc{person} category, which we manually added.

@@

\paragraph{Collection nodes}
We defined a set of \textit{collection nodes} which we would then use to collect our object instances from VG.

@@

\paragraph{Collection of instance candidates}
Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
The collection of such instances using the nodes was then straightforward: We retrieved all VG images  depicting an object whose name matches or is subsumed by one of the collection nodes. 
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{(REF to tagger)}, or that were multi-word expressions/phrases (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box\footnote{TODO: need to be clear from the general description of VG what is meant.} have an area of~$20-90\%$ of the whole image area.

@@

Table~\ref{tab:XXX} gives an overview of the collection nodes, XXX, XXX, grouped into $7$~domains. (\textbf{Report only dataset after round0, with a note in caption/footnote referring to the checkpoint pruning.})

@@

\begin{table*}
	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
	\toprule
	        animals\_plants &               vehicles &                        home &                clothing &                   buildings &                    food &                 people \\
	\midrule
	  ungulate.n.01 (2037) &  aircraft.n.01 (1208) &  furnishing.n.02 (5355) &  shirt.n.01 (968) &  house.n.01 (364) &  dish.n.02 (812) &  woman.n.01 (1768) \\
	 horse.n.01 (833) &  train.n.01 (957) &  vessel.n.03 (525) &  overgarment.n.01 (786) &  bridge.n.01 (297) &  baked\_goods.n.01 (770) &  man.n.01 (1167) \\
	  feline.n.01 (763) &  car.n.01 (727) &  kitchen\_utensil.n.01 (132) &  dress.n.01 (199) &  shelter.n.01 (169) &  foodstuff.n.02 (280) &  male\_child.n.01 (853) \\
	 dog.n.01 (688) &  motorcycle.n.01 (564) &  crockery.n.01 (92) &  headdress.n.01 (135) &  restaurant.n.01 (58) &  vegetable.n.01 (48) &  athlete.n.01 (396) \\
	  bird.n.01 (389) &  truck.n.01 (559) &  cutlery.n.02 (82) &  neckwear.n.01 (65) &  outbuilding.n.01 (31) &  edible\_fruit.n.01 (42) &  child.n.01 (333) \\
	  flower.n.01 (44) &  boat.n.01 (499) &  tool.n.01 (72) &  robe.n.01 (27) &  hotel.n.01 (19) &  beverage.n.01 (23) &  creator.n.02 (11) \\
	  rodent.n.01 (27) &  ship.n.01 (38) &  lamp.n.01 (34) &  glove.n.02 (7) &  housing.n.01 (17) &   &  professional.n.01 (5) \\
	 insect.n.01 (12) &   &   &  footwear.n.01 (5) &  place\_of\_worship.n.01 (12) &   &   \\
	  fish.n.01 (11) &   &   &   &   &   &   \\
	\bottomrule
\end{tabular}
	\caption{Overview of our dataset: Collection nodes for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset2}}
\end{table*}

@@

Overall $XX$~participants, each annotated between $XX$ and $XX$ instances.

\subsection{Data} give an overview of the collected data

>>>>

We take data from \vgenome \cite{krishna2016visualgenome}, which aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.

% \gbt{START to be refined -- taken from sivl submission as is}

% \vgenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
% It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.

% \begin{itemize}
%      		\item[(1)] \textbf{Specific categories}: are not available, as object categories and names are not consistently annotated (and even conflated)
% 				\item[(2)] \textbf{Exhaustive annotations}: are available, which is a huge advantage of this data sets
% 		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)

% \end{itemize}
% \gbt{END to be refined -- taken from sivl submission as is}

\subsection{Sampling of Instances (Images/Objects)}

We aimed at collecting a relatively large amount of naturalistic images (\textit{instances}) that depict common objects.
 % of frequent classes/names in  \vgenome, which, at the same time, have been frequently/commonly studied in the psycholinguistic literature. 
%Criteria: From CV: select images depicting objects with relatively frequent names; From CogSci: select objects which have been frequently studied in cognitive science/psychological norming studies; we chose McRae et al. as basis.
We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
We added the \textsc{person} category because it is very frequent category in \vgenome.

@@

\paragraph{Collection nodes}
% Standard taxonomies do not align well with name variability; for instance, people use more varied names for types of dogs than for types of cows, while both dogs and cows are mammals.
We defined a set of \textit{collection nodes} which we would then use to collect our object instances from VG.

@@

\paragraph{Collection of instance candidates}
Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
The collection of such instances using the nodes was then straightforward: We retrieved all VG images  depicting an object whose name matches or is subsumed by one of the collection nodes. 
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{(REF to tagger)}, or that were multi-word expressions/phrases (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box\footnote{TODO: need to be clear from the general description of VG what is meant.} had an area of~$20-90\%$ of the whole image area.

@@

Table~\ref{tab:XXX} gives an overview of the collection nodes, XXX, XXX, grouped into $7$~domains. (\textbf{Report only dataset after round0, with a note in caption/footnote referring to the checkpoint pruning.})
\gbt{I would put only a table with the final dataset, not the intermediate one (round0). That is, include a table with the 25K imgs (the 30K imgs were just our initial pool).}

@@

\begin{table*}
\small
	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
	\toprule
	        animals\_plants &               vehicles &                        home &                clothing &                   buildings &                    food &                 people \\
	\midrule
	  ungulate.n.01 (2037) &  aircraft.n.01 (1208) &  furnishing.n.02 (5355) &  shirt.n.01 (968) &  house.n.01 (364) &  dish.n.02 (812) &  woman.n.01 (1768) \\
	 horse.n.01 (833) &  train.n.01 (957) &  vessel.n.03 (525) &  overgarment.n.01 (786) &  bridge.n.01 (297) &  baked\_goods.n.01 (770) &  man.n.01 (1167) \\
	  feline.n.01 (763) &  car.n.01 (727) &  kitchen\_utensil.n.01 (132) &  dress.n.01 (199) &  shelter.n.01 (169) &  foodstuff.n.02 (280) &  male\_child.n.01 (853) \\
	 dog.n.01 (688) &  motorcycle.n.01 (564) &  crockery.n.01 (92) &  headdress.n.01 (135) &  restaurant.n.01 (58) &  vegetable.n.01 (48) &  athlete.n.01 (396) \\
	  bird.n.01 (389) &  truck.n.01 (559) &  cutlery.n.02 (82) &  neckwear.n.01 (65) &  outbuilding.n.01 (31) &  edible\_fruit.n.01 (42) &  child.n.01 (333) \\
	  flower.n.01 (44) &  boat.n.01 (499) &  tool.n.01 (72) &  robe.n.01 (27) &  hotel.n.01 (19) &  beverage.n.01 (23) &  creator.n.02 (11) \\
	  rodent.n.01 (27) &  ship.n.01 (38) &  lamp.n.01 (34) &  glove.n.02 (7) &  housing.n.01 (17) &   &  professional.n.01 (5) \\
	 insect.n.01 (12) &   &   &  footwear.n.01 (5) &  place\_of\_worship.n.01 (12) &   &   \\
	  fish.n.01 (11) &   &   &   &   &   &   \\
	\bottomrule
\end{tabular}
	\caption{Overview of our dataset: Collection nodes for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset2}}
\end{table*}

@@

Overall $XX$~participants, each annotated between $XX$ and $XX$ instances. \gbt{Put mean or median instead of min-max}

\subsection{Data}

give an overview of the collected data

### 2019-05-07 papers/EMNLP2019/relwork.tex
intro quite decent; minor fixes in other sections

\section{Related Work}
\label{sec:related}

@@

 Seminal work on concepts by Rosch suggests that object names typically exhibit a preferred level of specificity called the \textbf{entry-level}. This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \refexp{bird}, \refexp{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \refexp{sparrow}, \refexp{convertible}). However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}. 
%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in  
%with respect to the chose level of specificity. 
their choice of the level of specificity. 
Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases %\cite{rohde2012communicating} \cite{graf2016animal}. 
\cite{rohde2012communicating,graf2016animal}.

@@

State-of-the-art computer vision systems are able to classify images into thousands of different categories (e.g.\  \newcite{googlenet}). These object recognition systems are now widely used in vision \& language research.
Nevertheless, the way the treat object recognition is conceptually very simple (if not to say, naive):  standard object classification schemes are inherently ``flat'', and treat object labels as mutually exclusive \cite{deng2014large}, ignoring all kinds of linguistic relations between these labels and ignoring the fact that an object can easily be an instance of several categories.\cs{I would make this statement stronger and argue that \textbf{object recognition is merely a labeling of objects  with human interpretable symbols}, and that a system would probably fail if it had to decide whether an object labeled as, e.g.\ \refexp{fig} may also be labeled as \refexp{food}.}

@@

\newcite{Ordonez:2016} have studied the problem of deriving appropriate object names, or so-called entry-level
 categories, from the output of an object recognizer. Their approach focusses on linking abstract object categories in ImageNet to actual words via translation procedures that e.g. involve corpus frequencies. 
 \newcite{zarriess-schlangen:2017} learn a model of object naming on a corpus of referring expressions paired with objects in real-world images, but focus on combining visual and distributional information and on zero-shot learning.
 Thus, object naming is an important task for referring expression generation, though most research in this area has focussed on content and attribute selection \cite{Kazemzadeh2014,gkatzia:2015,zarrieschlang:easy-pre,Maoetal:cocorefexp}.

\paragraph{Existing resources and their shortcomings}
Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g. object labels are typically quite general as in Flickr30k \cite[e.g.,~\cat{people, animals, bodyparts, clothing}]{plummer2015flickr30kentities} or taxonomically heterogeneous as in MS COCO \cite[e.g.,~\cat{people, baseball glove, bird}]{mscoco}.

>>>>

@@

 Seminal work on concepts by Rosch and colleagues suggests that object names typically exhibit a preferred level of specificity, which \citet{jolicoeur1984pictures} called the \textbf{entry-level}. This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \refexp{bird}, \refexp{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \refexp{sparrow}, \refexp{convertible}). However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}. 
%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in  
%with respect to the chose level of specificity. 
their choice of the level of specificity. 
Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases %\cite{rohde2012communicating} \cite{graf2016animal}. 
\cite{rohde2012communicating,graf2016animal}.

@@

State-of-the-art computer vision systems are able to classify images into thousands of different categories (e.g.\  \newcite{googlenet}). These object recognition systems are now widely used in vision \& language research.
Nevertheless, the way the treat object recognition is conceptually very simple (if not to say, naive):  standard object classification schemes are inherently ``flat'', and treat object labels as mutually exclusive \cite{deng2014large}, ignoring all kinds of linguistic relations between these labels and ignoring the fact that an object can easily be an instance of several categories.\cs{I would make this statement stronger and argue that \textbf{object recognition is merely a labeling of objects  with human interpretable symbols}, and that a system would probably fail if it had to decide whether an object labeled as, e.g.\ \refexp{fig} may also be labeled as \refexp{food}.} \gbt{ok}

@@

\newcite{Ordonez:2016} have studied the problem of deriving appropriate object names, or so-called entry-level
 categories, from the output of an object recognizer. Their approach focusses on linking abstract object categories in ImageNet to actual words via translation procedures that e.g. involve corpus frequencies. 
 \newcite{zarriess-schlangen:2017} learn a model of object naming on a corpus of referring expressions paired with objects in real-world images, but focus on combining visual and distributional information and on zero-shot learning.
Object naming is also an important task for referring expression generation, though most research in this area has focussed on content and attribute selection \cite{Kazemzadeh2014,gkatzia:2015,zarrieschlang:easy-pre,Maoetal:cocorefexp}. \gbt{Should we put this as motivation also in the intro?}

% \paragraph{Existing resources and their shortcomings}
% Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g. object labels are typically quite general as in Flickr30k \cite[e.g.,~\cat{people, animals, bodyparts, clothing}]{plummer2015flickr30kentities} or taxonomically heterogeneous as in MS COCO \cite[e.g.,~\cat{people, baseball glove, bird}]{mscoco}.
